%-------------------------
% Resume in LateX
% Author : John Lunz
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemPlain}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\href{https://www.linkedin.com/in/john-lunz/}{\Large John Lunz}} & Email: \href{mailto:johnlunz8@gmail.com}{johnlunz8@gmail.com}\\
  \href{https://www.linkedin.com/in/john-lunz/}{LinkedIn - https://www.linkedin.com/in/john-lunz/} & Mobile: \href{tel:+15165228666}{+1-516-522-8666} \\
  \href{https://github.com/angrycolt84}{GitHub - https://github.com/angrycolt84}
\end{tabular*}



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {KKR}{Boston, MA}
      {Assistant Vice President, Backend Technology}{Dec 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Project Ownership}
          {Responsible for building new functionality and maintaining multiple mission critical modules across multiple languages and infrastructures for middle office operations.}
        \resumeItem{Integration}
          {Closely collobarated with multiple teams to integrate live application suite across multiple organizations including new security standards and AWS infrastructure impacting hundreds of users.}
        \resumeItem{Deployment}
          {Responsible for code reviewing junior engineers and deploying application suite worked on by 20+ developers using ServiceNow Change Management for production releases.}
        \resumeItem{AI Driven Development}
          {Utilized Claude Code to create multiple sub-agents to develop a new document generation application with React/Vite JS Front End and Python FastAPI backend.}
      \resumeItemListEnd
% --------Multiple Positions Heading------------
   \resumeSubSubheading
    {Backend Engineer III}{May 2025 -- Dec 2025}
    \resumeItemListStart
       \resumeItem{AI Driven ETL Middleware}
         {Built crucial confirmation middleware utilizing multiple AI and ML Models to convert PDF documentation into CSV files to then be ingested into Postgres database.}
       \resumeItem{Docusign Integration}
         {Created integration software with Docusign to batch submit many documents to then be docusigned replacing vendor software saving the firm thousands of dollars per month in software fees.}
       \resumeItem{Legacy Code Optimization}
         {Optimized legacy Bloomberg API to support runtime polymorphism and a configuration-driven approach saving ten hours in manual processing per month.}
    \resumeItemListEnd

%-------------------------------------------

    \resumeSubheading
      {Global Atlantic}{Brighton, MA}
      {Backend Engineer II}{Dec 2023 -- May 2025}
      \resumeItemListStart
        \resumeItem{Pipeline Optimization}
          {Optimized crucial data pipeline, combining stored procedures and custom UDFs with Python-based automation scripts improving processing speed by 95 percent.}
        \resumeItem{CI/CD}
          {Architected and maintained a lightweight CI/CD automation layer, leveraging git hooks, shell scripts, and automated test triggers to streamline code validation and deployment processes across environments.}
        \resumeItem{Transaction Automation}
          {Engineered an automated data pipeline using Pandas, Redshift Data Lake, and OAuth2 authenticated API microservices to gather, normalize, and stream high volume cash transaction data.}
        \resumeItem{Data Integrity}
          {Validated High Volume Cash Transaction Data to ensure data integrity at all pipeline steps for ten thousand plus transactions per month totalling well over two million dollars.}
      \resumeItemListEnd

    \resumeSubheading
      {FDM Group}{Boston, MA}
      {Backend Engineer}{Nov 2021 -- Dec 2023}
      \resumeItemListStart
        \resumeItem{Date Pipeline}
          {Built data ingestion pipeline with Python to process 10,000+ events per week in XML, JSON, and additional legacy formats replacing previously manual ingestion.}
        \resumeItem{SDLC}
          {Worked with end users to gather requirements, build minimum viable product, demo, and iterate in an agile manner.}
        \resumeItem{Middleware}
          {Improved vendor data processing by building middleware microservice to optimize heartbeat API connectivity necessary for millions of dollars of settled trades.}
        \resumeItem{Support}
          {Collobarated with Production Support and internal team members to efficiently address, debug, and fix production issues as part of regular on-call rotation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%  \resumeSubItem{QuantSoftware Toolkit}
 %     {Open source Python library for financial data analysis and machine learning for finance.}
  %  \resumeSubItem{GitHub Visualization}
   %   {Data visualization of Git log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step-by-step instructions on setting up developer environment on macOS.}
%  \resumeSubHeadingListEnd

%
%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{\textbf{Languages}{: Python, Mendix, SQL}}
    \item{\textbf{Technologies}{: AWS, Claude Code, FastAPI}}
  \resumeSubHeadingListEnd


%-------------------------------------------

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Fordham University}{Bronx, NY }
      {Bachelor of Science in Finance, Information Technology; GPA: 3.81}{Aug 2016 -- May 2020}
  \resumeSubHeadingListEnd

\end{document}
